Machine Learning and the Many-body Problem

### 2019-01-15 doc/MachineLearning/Article.tex
added ml paper

\title{Time-dependent optimized coupled-cluster method for multielectron dynamics}

\author{Håkon Emil Kristiansen}
\email[Electronic mail:]{haakoek@student.matnat.uio.no}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\begin{abstract}
We present a working implementation of a simplified version of the
orbital-adaptive time-dependent coupled-cluster method which we refer
to as just the time-dependent coupled-cluster (TDCC) method.
OATDCC/TDCC approximates solutions to the quantum $N$-body problem and
for $N=2$ TDCC is equivalent to the time-dependent
configuration-interaction method (TDCI).  A TDCI solver is implemented
and shown to be correct by comparing with a previous study and is then
used as a foundation for verifying the implementation of the TDCC
method. For one and two dimensional quantum dot systems with $N=2$ we
demonstrate that the methods are equal to numerical
precision. Furthermore, for a small number of basis functions we use
the TDCC solver to compute the time evolution of six-electron
isotropic quantum dot.
\end{abstract}

>>>>

\title{Machine Learning and the Many-body Problem}

\author{Jane Kim}
\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\author{Vilde Flugsrud}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\author{Sebastian G.~Winther-Larsen}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\author{Morten Hjorth-Jensen}
\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}

\begin{abstract}

\end{abstract}
